Towards Accelerating Deep Neural Network Training on FPGAs Facilitating the Use of Variable Precision

### 2018-07-02 SWoPP2018 Paper/paper.tex
Changed framework text.

\subsection{FPGA NN Framework}
A small framework was built, consisting of multiple kernels.
One simple forward propagation kernel with optional Relu activation function integrated into it and a forward softmax kernel.
\subsubsection{Design overview}
\Cref{fig:block-diagram} shows a overview of the system.
The backwards kernels are a work in progress, so for now we use an external training script.
The host code, written in python, does a kernel call for every layer.
And does a final softmax kernel call to get the final prediction.
For perfomance this could obviously be done on the host, given the limited size of most final layers, but performance is not the main goal of this effort.
The main goal to make replacing the numerical format easier, and thus all the calculations need to be done in that format, and an FPGA is better at accomodating that without a huge performance impact.

@@

\subsubsection{Design decisions}
One of the main choices with the largests effect on implementation is whenever to keep all weight matrices in memory transposed.
During inference this is very benificial, as this makes most reads sequential.
During training, using stochastic gradient descent, this can be a problem, the weight matrix should now be transposed back.
But since the artihmetic density of training is higher, the effect might be slightly less pronounced.

>>>>

\subsection{FPGA NN Framework}
The goal of this framework is generality, in so far that when finished one can select which numerical format one wants to use and then compile the OpenCL kernel for that format.
While keeping the same API, so easier comparative research can be done on training performance using the different formats.

\subsubsection{Design overview}
\Cref{fig:block-diagram} shows a overview of the system.
The backwards kernels are a work in progress, so for now we use an external training script.
The host code, written in python, does a kernel call for every layer.
And does a final softmax kernel call to get the final prediction.
For perfomance this could obviously be done on the host, given the limited size of most final layers, but performance is not the main goal of this effort.
The main goal to make replacing the numerical format easier, and thus all the calculations need to be done in that format, and an FPGA is better at accomodating that without a huge performance impact.

@@

\subsubsection{Design decisions}
One of the main choices with the largests effect on implementation is whenever to keep all weight matrices in memory transposed.
During inference this is very benificial, as this makes most reads sequential.
During training, using stochastic gradient descent, this can be a problem, the weight matrix should now be transposed back.
But since the artihmetic density of the training process is higher, the effect might be slightly less pronounced.
